---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 10,
  fig.retina = 3
)
```

# ggsegMcalt

<!-- badges: start -->
[![R-CMD-check](https://github.com/ggsegverse/ggsegMcalt/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ggsegverse/ggsegMcalt/actions/workflows/R-CMD-check.yaml)
[![r-universe](https://ggseg.r-universe.dev/badges/ggsegMcalt)](https://ggseg.r-universe.dev/ggsegMcalt)
<!-- badges: end -->

MCALT (Mayo Clinic Adult Lifespan Template) atlas for the ggseg ecosystem.

## Installation

We recommend installing the ggseg-atlases through the ggseg
[r-universe](https://ggseg.r-universe.dev/ui#builds):

```{r}
#| label: install-r-universe
#| eval: false
options(repos = c(
  ggseg = "https://ggseg.r-universe.dev",
  CRAN = "https://cloud.r-project.org"
))

install.packages("ggsegMcalt")
```

You can install this package from [GitHub](https://github.com/) with:

```r
# install.packages("pak")
pak::pak("ggsegverse/ggsegMcalt")
```

## Cortical atlas

```{r}
#| label: cortical
library(ggseg)
library(ggsegMcalt)

plot(mcalt_cortical())
```

## Subcortical atlas

```{r}
#| label: subcortical
plot(mcalt_subcortical())
```

## Data source

Schwarz CG et al. (2017). The Mayo Clinic Adult Lifespan Template (MCALT):
Better quantification across the lifespan. *Alzheimer's & Dementia*, 13(7),
P93-P94. [doi:10.1016/j.jalz.2017.06.1071](https://doi.org/10.1016/j.jalz.2017.06.1071)
